RAX:Efficiently Evaluating the Complexity of Porting for RISC-V

### 2024-01-29 Paper/latex1-27/paper.tex
Add files via upload

Many related works focus on the code complexity and portability evaluation,but studies for CPU architectures are currently lacking in these areas\cite{2016helei},\cite{TAHIR2016101},\cite{Sholiq_2021}.Du et al. have developed a basic statistical evaluation plan for CPU architecture code\citep{2023du}.However,their work lacks a thorough validity analysis of factors,and may not consider the complexity factors associated with the software operation and maintenance process.
To overcome these challenges, we propose RAX, an effective porting
complexity evaluation tool which accurately locates the CPU architecture code and calculates the code complexity of the software.The contributions of this paper are as follows:
\begin{itemize}
  \item We analysis the actual porting modifications and figure out one of the most important factors,Cyclomatic Complexity(CC), exploring its significant value in porting scenarios.
  % \item We explore building high-quality datasets that can cover various porting scenarios to solve the problem of imbalanced datasets of existing tools.Tuning machine learning models to address ambiguous identification of samples of medium and hard complexity compared to other studies.
  \item Based on architecture-related factors, we propose RAX, to efficiently assess the complexity of software during porting to the RISC-V.
  % \item We nearly doubled the dataset compared to other tool,and verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
  \item We build a dataset of real-world C/C++ projects and use it to evaluate the effectiveness of RAX.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
\end{itemize}
The remainder of this paper is organized as follows.In Section 2,we briefly analyze architecture-related factors. Section 3 presents the implementation and evaluation of RAX. Section 4 and 5 presents related work and conclusions.

@@

% To answer RQ 1,this section provides a validity analysis of porting-related factors on RAX.
% First,we try to use code complexity metrics to evaluate porting work.
% The software metrics of code Cyclomatic Complexity(CC) can help developers make macro judgments on software complexity and maintenance difficulty. By evaluating potential and hidden porting difficulties,code complexity helps the tool improve accuracy \cite{2005Exploring}.
% At present, CC indicators are mostly used in evaluating code quality, inspecting defect, reconstructing code, etc \cite{1991Cyclomatic}.
% During the porting process, developers will target a large number of project source codes,build scripts,assembly codes,and a macro understanding of the project is required in the early stage of porting.
% This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we discovered that even though architectural code can be separated quite clearly from common code, when faced with large-scale projects, we still require numerous iterative tests to uncover unknown architectural code. Building upon this, we study the quantification of the significance of cyclomatic complexity in porting work.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figure2.pdf}
  \caption{The Relationship between Score and CC}
  \label{fig:figure2}
  \Description{The Relationship between Score and CC}
\end{figure}
\subsection{Factor 1: Cyclomatic Complex(CC)}
\label{sec:factor-1}
First,we try to use code complexity metrics to evaluate porting work.
CC can help developers make macro judgments on software complexity and maintenance difficulty,and helps the tool improve accuracy \cite{2005Exploring}.
% At present, CC indicators are mostly used in evaluating code quality, inspecting defect, reconstructing code, etc \cite{1991Cyclomatic}.
During the porting process, developers will target a large number of project source codes,and a macro understanding of the project is required in the early stage of porting.This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we discovered that even though architectural code can be separated quite clearly from common code, when faced with large-scale projects, we still require numerous iterative tests to uncover unknown architectural code.
Based on the above, we use the lizard CC detection tool and optimize its functions.This paper proposes a new CC method:
 First, we calculate the function-level CC for all files in the project using McCabe's method. Following Liu's mention of System Cyclomatic Complexity (SCC) in software evolution assessment techniques based on code change detection \cite{liuhuihui00}, we define SCC as the total sum of function-level values in the system.
  Our CC calculation approach is expressed by equation (1) to (3),where lowercase cc represents the cyclomatic complexity at the function or file level.The uppercase CC represents the overall cyclomatic complexity of the software package,serving as a crucial factor in our tool.Here, |E| denotes the number of edges in the function control flow graph,and |N| represents the number of nodes.The function control flow graph is constructed based on branching structures such as if, while, and switch statements.

@@

Second, we consider the effectiveness of the architecture-related code structure proposed by other tool and conduct comparative experiments using more potential factors.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figure3.pdf}
  \caption{The Heat Map of Pearson Correlation}
  \label{fig:figure3}
  \Description{The Correlation}
\end{figure}
\subsection{Factor2:Arch\_code}

@@

\begin{table}
  \caption{Experimental Results of Models}
  \label{tab:evaluation}
  \begin{tabular}{ccccc}
    \toprule
     & Accuracy & Pmacro & Rmacro & F1macro \\
    \midrule
    Adaboost & 0.786 & 0.594 & 0.775 & 0.650 \\
    Random Forest & \textcolor{red}{0.857} & 0.817 & 0.873 & 0.836 \\
  \bottomrule
\end{tabular}
\end{table}

@@

After adding the code complexity factor and modifying the original model, RAX's result prediction accuracy is improved.
This is because code complexity can clearly distinguish three types of porting difficulty.
Motivation Chapters present the cause analysis.
Adding factors also makes RAX more robust and more friendly to projects with unbalanced complexity vectors.

@@

Chibios,u-boot are facing such a situation. Another reason is that we have added more medium or difficult complex samples to the data set to increase robustness and improve the innovativeness of the tool. Within evaluation, there are instances of inaccurate predictions. Analysis of some variations reveals that certain projects exhibit inherent complexity, entailing a substantial presence of architecture-specific code defined by Arch\_code.
Nevertheless, the practical porting process benefits from an array of auxiliary tools designed to support developers. In response to valuable suggestions from developers within the OpenEuler community, we conducted an evaluation of the porting complexity for various versions of the Chromium.Initially, we were able to accurately assess the porting complexity, yielding promising results. However, when it came to evaluating the work involved in iterative updates between versions, existing tools proved insufficient for precise estimation.Sometimes CPU architecture parts in projects are well separated from the common code,that just need only to adjust the moderate amount of code to recognize RISC-V,like nuttx.

>>>>

Many related works focus on the code complexity and portability evaluation,but studies for CPU architectures are currently lacking in these areas\cite{2016helei},\cite{TAHIR2016101},\cite{Sholiq_2021}.Du et al. have developed a basic statistical evaluation plan for CPU architecture code\citep{2023du}.However,their work lacks a thorough validity analysis of factors,and may not consider the complexity factors associated with the software operation and maintenance process.
To overcome these challenges, we propose RAX, an effective porting
complexity evaluation tool which accurately locates the CPU architecture code and calculates the code complexity of the software.The contributions of this paper are as follows:
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figure2.pdf}
  \caption{The Relationship between Score and CC}
  \label{fig:figure2}
  \Description{The Relationship between Score and CC}
\end{figure}
\begin{itemize}
  \item We analysis the actual porting modifications and figure out one of the most important factors,Cyclomatic Complexity(CC), exploring its significant value in porting scenarios.
  % \item We explore building high-quality datasets that can cover various porting scenarios to solve the problem of imbalanced datasets of existing tools.Tuning machine learning models to address ambiguous identification of samples of medium and hard complexity compared to other studies.
  \item Based on architecture-related factors, we propose RAX, to efficiently assess the complexity of software during porting to the RISC-V.
  % \item We nearly doubled the dataset compared to other tool,and verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
  \item We build a dataset of real-world C/C++ projects and use it to evaluate the effectiveness of RAX.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
\end{itemize}
The remainder of this paper is organized as follows.In Section 2,we briefly analyze architecture-related factors. Section 3 presents the implementation and evaluation of RAX. Section 4 and 5 presents related work and conclusions.

@@

% To answer RQ 1,this section provides a validity analysis of porting-related factors on RAX.
% First,we try to use code complexity metrics to evaluate porting work.
% The software metrics of code Cyclomatic Complexity(CC) can help developers make macro judgments on software complexity and maintenance difficulty. By evaluating potential and hidden porting difficulties,code complexity helps the tool improve accuracy \cite{2005Exploring}.
% At present, CC indicators are mostly used in evaluating code quality, inspecting defect, reconstructing code, etc \cite{1991Cyclomatic}.
% During the porting process, developers will target a large number of project source codes,build scripts,assembly codes,and a macro understanding of the project is required in the early stage of porting.
% This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we discovered that even though architectural code can be separated quite clearly from common code, when faced with large-scale projects, we still require numerous iterative tests to uncover unknown architectural code. Building upon this, we study the quantification of the significance of cyclomatic complexity in porting work.
% \begin{figure}
%   \centering
%   \includegraphics[width=\linewidth]{figure2.pdf}
%   \caption{The Relationship between Score and CC}
%   \label{fig:figure2}
%   \Description{The Relationship between Score and CC}
% \end{figure}
\subsection{Factor 1: Cyclomatic Complex(CC)}
\label{sec:factor-1}
First,we try to use code complexity metrics to evaluate porting work.
CC can help developers make macro judgments on software complexity and maintenance difficulty,and helps the tool improve accuracy \cite{2005Exploring}.
% At present, CC indicators are mostly used in evaluating code quality, inspecting defect, reconstructing code, etc \cite{1991Cyclomatic}.
During the porting process, developers will target a large number of project source codes,and a macro understanding of the project is required in the early stage of porting.This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we discovered that even though architectural code can be separated quite clearly from common code, when faced with large-scale projects, we still require numerous iterative tests to uncover unknown architectural code.
Based on the above, we use the lizard CC detection tool and optimize its functions.This paper proposes a new CC method:
 First, we calculate the function-level CC for all files in the project using McCabe's method. Following Liu's mention of System Cyclomatic Complexity (SCC) in software evolution assessment techniques based on code change detection \cite{liuhuihui00}, we define SCC as the total sum of function-level values in the system.
  Our CC calculation approach is expressed by equation (1) to (3),where lowercase cc represents the cyclomatic complexity at the function or file level.The uppercase CC represents the overall cyclomatic complexity of the software package,serving as a crucial factor in our tool.Here, |E| denotes the number of edges in the function control flow graph,and |N| represents the number of nodes.The function control flow graph is constructed based on branching structures such as if, while, and switch statements.

@@

Second, we consider the effectiveness of the architecture-related code structure proposed by other tool and conduct comparative experiments using more potential factors.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figure3.pdf}
  \caption{The Heat Map of Pearson Correlation}
  \label{fig:figure3}
  \Description{The Correlation}
\end{figure}
\subsection{Factor 2:Arch\_code}

@@

\begin{table}
  \caption{Results of Different Evaluation Tool}
  \label{tab:evaluation}
  \begin{tabular}{ccccc}
    \toprule
     & Accuracy & Pmacro & Rmacro & F1macro \\
    \midrule
    Adaboost & 0.786 & 0.594 & 0.775 & 0.650 \\
    Random Forest & \textcolor{red}{0.857} & 0.817 & 0.873 & 0.836 \\
  \bottomrule
\end{tabular}
\end{table}

@@

We conducted an in-depth analysis of the essential reasons for the improvement in accuracy after adding CC factors.This is because code complexity can clearly distinguish three types of porting difficulty.Adding factors also makes RAX more robust and more friendly to projects with unbalanced complexity vectors.

@@

Chibios,u-boot are facing such a situation. Another reason is that we have added more medium or difficult complex samples to the data set to increase robustness and improve the innovativeness of the tool. Within evaluation, there are instances of inaccurate predictions. (1)In cgal project, developers believe that some functions or performance improvements are only worth the effort in scenarios where users need them, and cgal can be made to work properly with a small amount of modifications.Since our tool traverses the global code,and optional information cannot be identified.(2)In PortAudio project, the improved portability is attributed to the existence of equivalent C language implementations for the assembly code. This has a significant impact on our evaluation results because RAX can not recognize the semantic meaning of the code.(3)Developers believe that dlib project has implemented distribution versions of multiple architectures, and the porting experience reduces the difficulty of porting.(4)Sometimes CPU architecture parts in projects are well separated from the common code,that just need only to adjust the moderate amount of code to recognize RISC-V,like nuttx project.
